Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-18 WSSSPE2_report/WSSSPE2_review.tex
Section 1: Warp lines.
no message

This report extends a previous report that discussed the submission, peer-review, and peer-grouping processes in detail.~\cite{WSSSPE2-pre-report}.  It is also based on a collaborative set
of notes taken through a google doc during the workshop~\cite{WSSSPE2-google-notes}.
Overall, the report discusses the organization work done before the workshop (\S\ref{sec:preworkshop}), the keynotes (\S\ref{sec:keynotes}), a session on defining sustainability (\S\ref{sec:defining}), the five breakout sessions---exploring sustainability (\S\ref{sec:exploring}); software development experiences (\S\ref{sec:devel}); credit \& incentives (\S\ref{sec:credit}); reproducibility, reuse, \& sharing (\S\ref{sec:reproduce}); code testing \& code review (\S\ref{sec:code_testing})---and some conclusions (\S\ref{sec:conclusions}).  The report also includes an incomplete list of attendees (Appendix \ref{sec:attendees}).

>>>>

This report extends a previous report that discussed the submission,
peer-review, and peer-grouping processes in detail~\cite{WSSSPE2-pre-report}.
It is also based on a collaborative set of notes taken through a google doc
during the workshop~\cite{WSSSPE2-google-notes}. Overall, the report discusses
the organization work done before the workshop (\S\ref{sec:preworkshop}); the
keynotes (\S\ref{sec:keynotes}); a session on defining sustainability
(\S\ref{sec:defining}); five breakout sessions that explored sustainability
(\S\ref{sec:exploring}); software development experiences (\S\ref{sec:devel});
credit \& incentives (\S\ref{sec:credit}); reproducibility, reuse, \& sharing
(\S\ref{sec:reproduce}); code testing \& code review
(\S\ref{sec:code_testing}); and some conclusions (\S\ref{sec:conclusions}). The
report also includes an incomplete list of attendees (Appendix~\ref{sec:attendees}).
